Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-01-09 03_marlin_paper.qmd
prepping repo for submission

---
title: "Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics"
author:
    - Daniel Ovando
    - Darcy Bradley
    - Echelle Burns
    - Lennon Thomas
    - James Thorson
date: "Updated `r Sys.Date()`"
format:
  pdf:
    toc: true
    fig-pos: 'H'
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
bibliography: references.bib
params:
  run_name: ["v0.3"]
abstract: "Abstract: Designing effective spatial management strategies is challenging because marine ecosystems are highly dynamic and opaque, and extractive entities such as fishing fleets respond endogenously to ecosystem changes in ways that depend upon ecological and policy context. We present a tool, `marlin`, that can be used to efficiently simulate the bio-economic dynamics of marine systems in support of both management and research. We demonstrate `marlin’s` capabilities by focusing on two case studies on the conservation and food production impacts of marine protected areas (MPAs): a coastal coral reef and a pelagic tuna fishery. In the coastal coral reef example, we explore how heterogeneity in species distributions and fleet preferences can affect distributional outcomes of MPAs. In the pelagic case study, we show how our model can be used to assess the climate resilience of different MPA design strategies, as well as the climate sensitivity of different fishing fleets. This paper demonstrates how intermediate complexity simulation of coupled bio-economic dynamics can help communities predict and potentially manage trade-offs between conservation, fisheries yields, and distributional outcomes of management policies affected by spatial bio-economic dynamics."
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
---

@@

source(here::here("scripts", "00_setup.R"))

@@

@@

@@

Each of the case studies contains too many parameters and options to be
succinctly presented in the text here, and we are concerned that
attempting to duplicate all of the parameters of the model here would
simply introduce error. As such, readers should consult the accompanying
code (xx provide clear instructions for which files xx) to view the
precise details of each simulation. Targeted tactical applications must
carefully consider and document all decisions made around model
parameters.

#### Rule-of-thumb MPA Design Strategies

@@

1.  Depletion Rate (*rate*): MPAs are placed based on the pre-MPA
    depletion-weighted catch relative to the total catch in a patch. So,
    patches with high rates of catch of depleted species relative to
    total catch are prioritized.

2.  Target Fishing (*target_fishing*): MPAs locations are prioritized
    proportional to fishery catches. Patches with high total
    catches are prioritized over patches with low catches.

@@

```{r}
#| label: fig-coral
#| fig-cap: "Distribution of fish spawning biomass (color) each season (row) under unfished conditions. The x-axis represents longitude, y-axis latitude. Numbers show the approximate location of each fleet's port. Rows indicate quarterly seasons that repeat each year."

@@

patch_biomass %>%
  group_by(critter, step) %>%
  mutate(sbiomass = biomass / max(biomass)) %>%
  ungroup() %>%
  filter(between(step,1,2)) %>% 
  mutate(Season = step) %>% 
  ggplot()+
  geom_tile(aes(x,y, fill = sbiomass),show.legend = FALSE) +
  geom_text_repel(data = coral_ports, aes(x, y, label = fleet), color = "red") +
  facet_grid(Season~critter) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_viridis_c() + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank())

@@

critter_biomass %>%
  ungroup() %>% 
  left_join(sci_to_com, by = "critter") %>%
  select(-critter) %>%
  rename(critter = common_name) %>%
  ggplot(aes(step, depletion, color = critter)) +
  geom_line(linewidth = 1) +
  scale_y_continuous(limits = c(0, 1), name = "Depletion", expand = expansion(mult = c(0.0,0.05))) +
  scale_x_continuous(name = "Time Step") +
  scale_color_discrete(name = "")

@@

For the coastal coral reef example the *target_fishing* MPA design strategies was capable of producing a Pareto-improving, i.e. potentially win-win, outcome where the total
spawning biomass divided by unfished spawning biomass across all species
increase by up to 200% while maintaining at least the same levels of
fisheries yields as would be caught in the absence of any MPAs.
Conversely, achieving increases in total fish biomass through the *rate* strategy resulted in immediate losses in total yields, and in losses to both yields and total biomass in some cases
(@fig-coral-results).

@@

The *rate* MPA placement strategy produced
lower total fishery gains but minimized the negative impacts on fleet
two. However, this strategy produced much lower conservation gains
than the *target_fishing* strategy, only benefiting
deep snapper meaningfully, and in fact resulting in slight losses to the
nearshore snapper and grouper populations for MPA sizes less than roughly 75% of the
simulated space. The *target_fishing* strategy
resulted in rapid conservation gains across all of the simulated
species.

@@

```{r}
#| label: fig-coral-results
#| fig-cap: "Frontier in conservation and yield outcomes under different MPA design strategies (A) for coastal coral reef case study. Change in yield for each fleet (B) and depletion per species (C) as a function of MPA size and MPA design strategy for the coral reef case study."
#| fig-height: 4
#| fig-width: 6

@@

coral_frontier <- coral_results %>% 
  group_by(prop_mpa, placement_strategy) %>% 
  summarise(biodiv = sum(biodiv), yield = sum(yield)) %>% 
  group_by(placement_strategy) %>% 
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1,
         delta_biodiv = biodiv / biodiv[prop_mpa == 0] - 1) %>% 
  ggplot(aes(delta_biodiv, delta_yield, color = placement_strategy)) + 
  geom_vline(aes(xintercept = 0), linetype = 2) +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line() + 
  scale_x_continuous(name = "Change in Total Depletion", labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Change in Yield", labels = scales::label_percent(accuracy = 1)) + 
  scale_color_ordinal(name = '')+
  guides(color = guide_legend(nrow = 4)) + 
  labs(tag = "A") + 
  theme(
    legend.position = c(0.7, 1),
    legend.background = element_rect(fill = "transparent"),
    legend.text = element_text(size = 8)
  )

coral_fleet_yield <- coral_results %>%
  pivot_longer(starts_with("fleet_"),
               names_to = "fleet",
               values_to = "fleet_yield") %>%
  group_by(prop_mpa, fleet, placement_strategy) %>%
  summarise(yield = sum(fleet_yield), biodiv = sum(unique(biodiv))) %>%
  group_by(fleet, placement_strategy) %>%
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1) %>%
  ggplot(aes(prop_mpa, delta_yield, color = fleet)) +
    geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line() +
  facet_wrap( ~ placement_strategy) +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_y_continuous(name = "Yield",
                     labels = scales::label_percent(accuracy = 1)) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8))  + 
    scale_color_discrete(name = '') + 
    labs(tag = "B")

coral_critter_bio <- coral_results %>%
  group_by(prop_mpa, critter, placement_strategy) %>%
  summarise(biodiv = sum(unique(biodiv))) %>%
  group_by(critter, placement_strategy) %>%
  mutate(delta_bio = biodiv) %>%
  # filter(prop_mpa < 0.4) %>% 
  ggplot(aes(prop_mpa, pmin(Inf,delta_bio), color = critter)) +
  geom_line() +
  facet_wrap( ~ placement_strategy) +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1),
                     guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Depletion") + 
  scale_color_viridis_d(name = '', option = "C") + 
    labs(tag = "C") + 
  theme(axis.text = element_text(size = 8))

((coral_frontier + plot_layout(guides = "keep")) | (coral_fleet_yield / coral_critter_bio) + plot_layout(guides = "collect")) & theme(strip.text = element_text(size  = 8), plot.margin = margin(.1, .1, .1, .1, "cm"), legend.text = element_text(size = 7))

@@

The yield impacts of the proposed MPA strategies were much more
sensitive to climate impacts for the purse seine fishery. Under the
*status quo* species distribution, the *target_fishing* MPA design
strategy produced increases in fisheries yields at sizes between 25-50%
of the simulated area; that same MPA network resulted in the near
complete loss of yields from the purse seine fleet when applied to the
climate change scenario. In contrast, the yield outcomes for the
longline fleet were relatively insensitive to the simulated range shifts
(@fig-blue-results).

From a conservation perspective, species such as albacore and swordfish
were relatively insensitive to the simulated range shifts, whereas
species such as bigeye tuna and silky shark showed extreme variation in
outcomes depending on the climate scenario. For bigeye tuna, under the
*status quo* conditions the *target_fishing* MPA design strategy
resulted in rapid increases in the population, but that same MPA network produced much smaller and slower gains under climate change.
However, for blue sharks this trend is inverted, with more rapid
conservation gains under the range shift scenario than the *status quo*
(@fig-blue-results).

@@

blue_fleet_yield <- blue_water_results %>%
  filter(placement_strategy %in% c("target_fishing", "rate")) %>%
  pivot_longer(names(blue_fleets),
               names_to = "fleet",
               values_to = "fleet_yield") %>%
  group_by(prop_mpa, fleet, placement_strategy, climate) %>%
  summarise(yield = sum(fleet_yield), biodiv = sum(unique(biodiv))) %>%
  group_by(fleet, placement_strategy) %>%
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1) %>%
  ggplot(aes(prop_mpa, delta_yield, color = climate)) +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line(size = linesize, show.legend = FALSE) +
  facet_grid(fleet ~ placement_strategy, scales = "free_y") +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_y_continuous(name = "Change in Yield",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_color_manual(
    values = c("#63B8FF", "#FF4500"),
    labels = c("Status Quo", "Range Shift"),
    name = ''
  ) + 
  theme(strip.text = element_text(size = 8)) + 
  labs(tag = "A")

blue_critter_bio <- blue_water_results %>%
    filter(placement_strategy %in% c("target_fishing", "rate")) %>% 
  group_by(prop_mpa, critter, placement_strategy, climate) %>%
  summarise(biodiv = sum(unique(biodiv))) %>%
  group_by(critter, placement_strategy) %>%
  mutate(delta_bio = biodiv) %>%
  ggplot(aes(prop_mpa, pmin(1,delta_bio), color = climate, linetype = placement_strategy)) +
  geom_line(size = linesize) + 
  facet_wrap(~critter) +
  scale_color_manual(values = c("#63B8FF","#FF4500"), labels = c("Status Quo","Range Shift"), name = '') +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Change in Spawning Biomass",limits = c(0, NA)) +
  scale_linetype(name = "MPA Strategy") + 
    labs(tag = "B")+
  theme(strip.text = element_text(size = 7),
        axis.text.y = element_text(size = 6))

# blue_frontier / blue_critter_bio + plot_layout(heights = c(1,2))
(blue_fleet_yield / 
blue_critter_bio) + plot_layout(heights = c(1.5,2), guides = "collect" )
```

@@

@@

# Scraps

>>>>

---
title: "Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics"
author:
    - Daniel Ovando
    - Darcy Bradley
    - Echelle Burns
    - Lennon Thomas
    - James Thorson
date: "Updated `r Sys.Date()`"
format:
  pdf:
    toc: true
    fig-pos: 'H'
  html: default
  docx: default
execute:
  echo: false
  message: false
  warning: false
  cache: false
bibliography: references.bib
params:
  run_name: ["v0.5"]
abstract: "Abstract: Designing effective spatial management strategies is challenging because marine ecosystems are highly dynamic and opaque, and extractive entities such as fishing fleets respond endogenously to ecosystem changes in ways that depend upon ecological and policy context. We present a tool, `marlin`, that can be used to efficiently simulate the bio-economic dynamics of marine systems in support of both management and research. We demonstrate `marlin’s` capabilities by focusing on two case studies on the conservation and food production impacts of marine protected areas (MPAs): a coastal coral reef and a pelagic tuna fishery. In the coastal coral reef example, we explore how heterogeneity in species distributions and fleet preferences can affect distributional outcomes of MPAs. In the pelagic case study, we show how our model can be used to assess the climate resilience of different MPA design strategies, as well as the climate sensitivity of different fishing fleets. This paper demonstrates how intermediate complexity simulation of coupled bio-economic dynamics can help communities predict and potentially manage trade-offs between conservation, fisheries yields, and distributional outcomes of management policies affected by spatial bio-economic dynamics."
header-includes:
  - \usepackage{setspace}\doublespacing
  - \usepackage{lineno}\linenumbers
---

@@

source(here::here("00_setup.R"))

@@

# simple function to make prettier labels
titler <- function(x){

  stringr::str_to_title(stringr::str_replace_all(x,"_"," "))

@@

We define a few commonly used terms here. *Yields* refers to the volume of catch from fishing activity. *Spawning stock biomass* refers to the total biomass of reproductively mature fish in the water, a function of numbers, weight, and sexual maturity at age. *Depletion* is a common term in the fisheries literature, and reflects here the *spawning stock biomass* in a given time step relative to *unfished spawning stock biomass*. So, a depletion value of 1 means that the population is unfished, a depletion value of 0 means the population is extinct.

@@

Each of the case studies contains too many parameters and options to be
succinctly presented in the text here, and we are concerned that
attempting to duplicate all of the parameters of the model here would
simply introduce error. As such, readers should consult the accompanying
code to view the
precise details of each simulation. Targeted tactical applications must
carefully consider and document all decisions made around model
parameters.

#### MPA Design Strategies

@@

1.  *Rate*: MPAs are placed based on the pre-MPA
    depletion-weighted catch relative to the total catch in a patch. So,
    patches with high rates of catch of depleted species relative to
    total catch are prioritized.

2.  *Target Fishing*: MPAs locations are prioritized
    proportional to fishery catches. Patches with high total
    catches are prioritized over patches with low catches.

@@

```{r}
#| label: fig-coral
#| fig-cap: "Distribution of fish spawning biomass (cell color, yellow = higher, blue = lower) each season (columns) under unfished conditions. The x-axis represents longitude, y-axis latitude. Numbers show the approximate location of each fleet's (one or two) port. Columns indicate quarterly seasons that repeat each year."

@@

 patch_biomass %>%
  group_by(critter, step) %>%
  mutate(sbiomass = biomass / max(biomass)) %>%
  ungroup() %>%
  filter(between(step,1,2)) %>%
  mutate(step = fct_recode(as.factor(step), "2" = "1.25", "3" = "1.5", "4" = "1.75")) %>% 
  mutate(Season = step) %>% 
  ggplot()+
  geom_tile(aes(x,y, fill = sbiomass),show.legend = FALSE) +
  geom_text_repel(data = coral_ports, aes(x, y, label = fleet), color = "red") +
  facet_grid(critter~Season, labeller = labeller(critter = titler, Season = label_both)) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand = c(0,0)) +
  scale_fill_viridis_c() + 
  theme(axis.text = element_blank(),
        axis.ticks = element_blank(),
        axis.title = element_blank(),
        axis.line = element_blank())

@@

# critter_biomass %>%
#   ungroup() %>% 
#   left_join(sci_to_com, by = "critter") %>%
#   select(-critter) %>%
#   rename(critter = common_name) %>%
#   ggplot(aes(step, depletion, color = critter)) +
#   geom_line(linewidth = 1) +
#   scale_y_continuous(limits = c(0, 1), name = "Depletion", expand = expansion(mult = c(0.0,0.05))) +
#   scale_x_continuous(name = "Time Step") +
#   scale_color_discrete(name = "")

critter_biomass %>%
  ungroup() %>% 
  left_join(sci_to_com, by = "critter") %>%
  select(-critter) %>%
  rename(critter = common_name) %>%
  filter(step == max(step)) %>% 
  ggplot(aes(reorder(critter, depletion), depletion)) +
  geom_col() +
  scale_y_continuous(limits = c(0, 1), name = "Depletion", expand = expansion(mult = c(0.0,0.05))) +
  labs(x = "") + 
  coord_flip()

@@

For the coastal coral reef example the *Target fishing* MPA design strategies was capable of producing a Pareto-improving, i.e. potentially win-win, outcome where the total
spawning biomass divided by unfished spawning biomass across all species
increase by up to 200% while maintaining at least the same levels of
fisheries yields as would be caught in the absence of any MPAs.
Conversely, achieving increases in total fish biomass through the *Rate* strategy resulted in immediate losses in total yields, and in losses to both yields and total biomass in some cases
(@fig-coral-results).

@@

The *Rate* MPA placement strategy produced
lower total fishery gains but minimized the negative impacts on fleet
two. However, this strategy produced much lower conservation gains
than the *Target Fishing* strategy, only benefiting
deep snapper meaningfully, and in fact resulting in slight losses to the
nearshore snapper and grouper populations for MPA sizes less than roughly 75% of the
simulated space. The *Target Fishing* strategy
resulted in rapid conservation gains across all of the simulated
species.

@@

```{r}
#| label: fig-coral-results
#| fig-cap: "Percent change in yield per fleet (A) and depletion per species (B) as a function of MPA size and MPA design strategy for the coastal coral reef case study. Percent change in total yield across both fleets (y-axis) and total depletion across all species (x-axis) by MPA size (point size) and placement strategy (point color) (C)." 
#| fig-height: 4
#| fig-width: 6

@@

coral_frontier <- coral_results %>% 
  group_by(prop_mpa, placement_strategy) %>% 
  summarise(biodiv = sum(biodiv), yield = sum(yield)) %>% 
  group_by(placement_strategy) %>% 
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1,
         delta_biodiv = biodiv / biodiv[prop_mpa == 0] - 1) %>% 
  ungroup() %>% 
    mutate(placement_strategy= fct_relabel(placement_strategy, titler)) %>% 
  ggplot(aes(delta_biodiv, delta_yield, fill = placement_strategy, size = prop_mpa)) + 
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_point(alpha = 0.8, shape = 21) + 
  scale_x_continuous(name = "Change in Total Depletion", labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Change in Yield", labels = scales::label_percent(accuracy = 1)) + 
  scale_fill_viridis_d(name = '')+
  scale_size(name = "MPA Size", labels = scales::label_percent(accuracy = 1), breaks = seq(0.25,1, by = 0.25)) +
  guides(fill = guide_legend(order = 1, override.aes = list(size = 4)),
         size = guide_legend(order = 2, ncol = 2, byrow = TRUE)) + 
  labs(tag = "C")  + 
  theme(
    legend.position = c(0.725, .85),
    legend.background = element_rect(fill = "transparent", color = "black"),
    legend.text = element_text(size = 8)
  )

coral_fleet_yield <- coral_results %>%
  pivot_longer(starts_with("fleet_"),
               names_to = "fleet",
               values_to = "fleet_yield") %>%
  group_by(prop_mpa, fleet, placement_strategy) %>%
  summarise(yield = sum(fleet_yield), biodiv = sum(unique(biodiv))) %>%
  group_by(fleet, placement_strategy) %>%
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1) %>%
  ungroup() %>% 
  mutate(fleet= fct_relabel(fleet, titler)) %>% 
  ggplot(aes(prop_mpa, delta_yield, color = fleet)) +
    geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line() +
  facet_wrap( ~ placement_strategy, labeller = labeller(placement_strategy = titler)) +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_y_continuous(name = "Yield",
                     labels = scales::label_percent(accuracy = 1)) + 
  theme(axis.text.x = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8))  + 
    scale_color_discrete(name = '') + 
    labs(tag = "A")

coral_critter_bio <- coral_results %>%
  group_by(prop_mpa, critter, placement_strategy) %>%
  summarise(biodiv = sum(unique(biodiv))) %>%
  group_by(critter, placement_strategy) %>%
  mutate(delta_bio = biodiv) %>%
  mutate(critter = fct_relabel(critter, titler)) %>% 
  # filter(prop_mpa < 0.4) %>% 
  ggplot(aes(prop_mpa, pmin(Inf,delta_bio), color = critter)) +
  geom_line() +
  facet_wrap( ~ placement_strategy, labeller = labeller(placement_strategy = titler)) +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1),
                     guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Depletion") + 
  scale_color_brewer(name = '', type = "qual", palette = "Dark2") + 
    labs(tag = "B") + 
  theme(axis.text = element_text(size = 8), axis.text.x = element_text(size = 8))

((coral_fleet_yield / coral_critter_bio) | (coral_frontier + plot_layout(guides = "keep")) ) & theme(strip.text = element_text(size  = 8), plot.margin = margin(.1, .1, .1, .1, "cm"), panel.spacing = unit(1, "lines"), legend.text = element_text(size = 7))

@@

The yield impacts of the proposed MPA strategies were much more
sensitive to climate impacts for the purse seine fishery. Under the
*status quo* species distribution, the *Target Fishing* MPA design
strategy produced increases in fisheries yields at sizes between 25-50%
of the simulated area; that same MPA network resulted in the near
complete loss of yields from the purse seine fleet when applied to the
climate change scenario. In contrast, the yield outcomes for the
longline fleet were relatively insensitive to the simulated range shifts
(@fig-blue-results).

From a conservation perspective, species such as albacore and swordfish
were relatively insensitive to the simulated range shifts, whereas
species such as bigeye tuna and silky shark showed extreme variation in
outcomes depending on the climate scenario. For bigeye tuna, under the
*status quo* conditions the *Target Fishing* MPA design strategy
resulted in rapid increases in the population, but that same MPA network produced much smaller and slower gains under climate change.
However, for blue sharks this trend is inverted, with more rapid
conservation gains under the range shift scenario than the *status quo*
(@fig-blue-results).

@@

blue_fleet_yield <- blue_water_results %>%
  filter(placement_strategy %in% c("target_fishing", "rate")) %>%
  pivot_longer(names(blue_fleets),
               names_to = "fleet",
               values_to = "fleet_yield") %>%
  group_by(prop_mpa, fleet, placement_strategy, climate) %>%
  summarise(yield = sum(fleet_yield), biodiv = sum(unique(biodiv))) %>%
  group_by(fleet, placement_strategy) %>%
  mutate(delta_yield = yield / yield[prop_mpa == 0] - 1) %>%
  ggplot(aes(prop_mpa, delta_yield, color = climate)) +
  geom_hline(aes(yintercept = 0), linetype = 2) +
  geom_line(size = linesize, show.legend = FALSE) +
  facet_grid(fleet ~ placement_strategy, scales = "free_y", labeller = labeller(fleet = titler, placement_strategy = titler)) +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_y_continuous(name = "Change in Yield",
                     labels = scales::label_percent(accuracy = 1)) +
  scale_color_manual(
    values = c("#63B8FF", "#FF4500"),
    labels = c("Status Quo", "Range Shift"),
    name = ''
  ) + 
  theme(strip.text = element_text(size = 8)) + 
  labs(tag = "A")

blue_critter_bio <- blue_water_results %>%
    filter(placement_strategy %in% c("target_fishing", "rate")) %>% 
  group_by(prop_mpa, critter, placement_strategy, climate) %>%
  summarise(biodiv = sum(unique(biodiv))) %>%
  group_by(critter, placement_strategy) %>%
  mutate(delta_bio = biodiv) %>%
  ungroup() %>% 
  mutate(placement_strategy = fct_relabel(as.factor(placement_strategy), titler)) %>% 
  ggplot(aes(prop_mpa, pmin(1,delta_bio), color = climate, linetype = placement_strategy)) +
  geom_line(size = linesize) + 
  facet_wrap(~critter) +
  scale_color_manual(values = c("#63B8FF","#FF4500"), labels = c("Status Quo","Range Shift"), name = '') +
  scale_x_continuous(name = "MPA Size",
                     labels = scales::label_percent(accuracy = 1), guide = guide_axis(n.dodge = 2)) +
  scale_y_continuous(name = "Depletion",limits = c(0, NA)) +
  scale_linetype(name = "MPA Strategy") + 
    labs(tag = "B")+
  theme(strip.text = element_text(size = 7),
        axis.text.y = element_text(size = 6))

# blue_frontier / blue_critter_bio + plot_layout(heights = c(1,2))
(blue_fleet_yield / 
blue_critter_bio) + plot_layout(heights = c(1.5,2))
```

@@

# Data Availability Statement

All code and materials needed to reproduce this paper is available at (https://github.com/DanOvando/marlin-paper)[https://github.com/DanOvando/marlin-paper].

@@

### 2023-01-09 README.Rmd
circilng towards something
prepping repo for submission

@@

3. Make sure you have all dependencies installed by opening R and running `renv::restor()`

4. In the terminal, run `RUN_NAME:MyRunName FORMAT:MyFormat make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, docx

5. Wait for a bit! This command will run all the required scripts and knit the paper.

>>>>

## Navigating Repo

THe main scripts needed to reproduce results are

1. 00_setup.R
2. 01_coral_case_study.R
3. 02_blue_water_cast_study.R
4. 03_marlin_paper.qmd

The best way to reproduce the results is through the `make` commands described below. To reproduce results manually, first open 00_setup.R and set parameters as desired. Then, run 01_.. 02_... and 03_.

@@

3. Make sure you have all dependencies installed by opening R and running `renv::restore()`

4. In the terminal, run `RUN_NAME:MyRunName FORMAT:MyFormat make` where MyRunName is the name of the folder you want to create to store results (e.g. v0.1) and FORMAT is one of pdf, html, or docx

5. Wait for a bit! This command will run all the required scripts and knit the paper. Should take no more than a few hours.
